Risk and Trust in Open Systems:\\ \Large Towards formalising Permission and Authority, and specifying policies for Object Capability Patterns

### 2017-09-08 shupeng_msc_report.tex
update

In the DOM Tree example above, we simulate initialising a webpage with a root \sf{document} node that we set the property of a map-key "title" having a map-value of "Alice website". We then create a node for an advertisement called \sf{adnode}. To allow the external party the authority to modify the properties of \sf{adnode}, we create a restricted node object \sf{radnode} with a depth level of 0 that points to \sf{adnode}. In the simulation, we execute a method \sf{ad\_lambda} that attempts to call code on \sf{radnode}, where in our simulation, \sf{ad\_lambda} attempts to modify the root \sf{Document} node's properties by attempting to change the value of the root node's map-key "title", to "Bob's website". This would fail, because we have constructed \sf{radnode} with a depth level of 0, so we know that \sf{radnode} will not be able to traverse up to the root node of the tree. Therefore, we know the title of the root\sf{document} node remains intact as "Alice website" after execution of \sf{ad\_lambda}.
\begin{minipage}{\textwidth}
\subsubsection{DOM Tree Pattern Illustration}\label{sec:figdom}
\raggedright \small Here, we illustrate in more detail the example of the DOM Tree pattern in a visual diagram. Code can be found in found in \cref{sec:code_DOM}\\
\centering
\includegraphics[width=1.05\textwidth]{figures/DOM.pdf}
 \captionof{figure}{DOM Tree Example}\label{fig:figdom}
\end{minipage}
\clearpage

@@

\clearpage
\subsubsection{Policies for Caretaker Pattern}\label{sec:caretakerpolicies}
Here we show the important policies for the Caretaker pattern, where we also say how the Caretaker might leak paths in \textbf{Policy [Possible Leaked Paths from Caretaker]}. Path leakage is possible because the caretaker might possibly return the capability of its protected object o$'$ from some method call forwarded to o$'$, when o$'$ has a method that exposes its own capability; i.e. the caretaker does not create deep attenuating objects to mask capabilities returned by its protected object, or messages containing capabilities passed by its caller.\\

@@

\begin{minipage}{\textwidth}
\subsubsection{Caretaker Pattern Illustration}\label{sec:figcaretaker}
\centering
\includegraphics[width=1.05\textwidth]{figures/Caretaker.pdf}
 \captionof{figure}{Caretaker Pattern}
  \label{fig:figcaretaker}
\end{minipage}
\clearpage
\subsubsection{Policies for Membrane Pattern}\label{sec:membranepolicies}
Here we show the important policies for the Membrane pattern. Unlike the Caretaker pattern, a Membrane does not leak capabilities because the membrane creates deep attenuating new membranes to mask capabilities returned by its protected object, and capabilities in messages passed by its caller.\\

Every membrane and lock object has a ghost field \sf{parent}: \begin{itemize}
\item The ghost field \sf{parent} of a membrane object \sf{m$'$} points to a membrane \sf{m} if the constructor for \sf{m$'$} is called  by \sf{m}, otherwise it points to \sf{null}
\item The ghost field \sf{parent} of a lock object \sf{k$'$} points to a lock \sf{k} if the constructor for \sf{k$'$} is called by a membrane \sf{m}, where \sf{m.lock = k}, otherwise it points to \sf{null}
\end{itemize}

@@

\begin{minipage}{\textwidth}
\subsubsection{Membrane Pattern Illustration}\label{sec:figmem}
\centering
\includegraphics[width=1.05\textwidth]{figures/Membrane.pdf}
 \captionof{figure}{Membrane Pattern}
   \label{fig:figmem}
\end{minipage}
\section{Case Study of Ethereum / Solidity as a Non-OCap Model}\label{sec:ethereum}

>>>>

In the DOM Tree example above, we simulate initialising a webpage with a root \sf{document} node that we set the property of a map-key "title" having a map-value of "Alice website". We then create a node for an advertisement called \sf{adnode}. To allow the external party the authority to modify the properties of \sf{adnode}, we create a restricted node object \sf{radnode} with a depth level of 0 that points to \sf{adnode}. In the simulation, we execute a method \sf{ad\_lambda} that attempts to call code on \sf{radnode}, where in our simulation, \sf{ad\_lambda} attempts to modify the root \sf{Document} node's properties by attempting to change the value of the root node's map-key "title", to "Bob's website". This would fail, because we have constructed \sf{radnode} with a depth level of 0, so we know that \sf{radnode} will not be able to traverse up to the root node of the tree. Therefore, we know the title of the root\sf{document} node remains intact as "Alice website" after execution of \sf{ad\_lambda}.
\begin{minipage}{\textwidth}
\subsubsection{DOM Tree Pattern - Illustration}\label{sec:figdom}
\small Here, we illustrate in more detail an example of the DOM Tree pattern. The code can be found in \cref{sec:code_DOM}.\\
\includegraphics[width=\textwidth]{figures/DOM.pdf}
 \captionof{figure}{DOM Tree Example}\label{fig:figdom}
\end{minipage}
\clearpage

@@

\clearpage
\subsubsection{Caretaker Pattern - Policies}\label{sec:caretakerpolicies}
Here we show the important policies for the Caretaker pattern, where we also say how the Caretaker might leak paths in \textbf{Policy [Possible Leaked Paths from Caretaker]}. Path leakage is possible because the caretaker might possibly return the capability of its protected object o$'$ from some method call forwarded to o$'$, when o$'$ has a method that exposes its own capability; i.e. the caretaker does not create deep attenuating objects to mask capabilities returned by its protected object, or messages containing capabilities passed by its caller.\\

@@

\begin{minipage}{\textwidth}
\subsubsection{Caretaker Pattern - Illustration}\label{sec:figcaretaker}
\small Here, we illustrate in more detail an example of the Caretaker pattern. The code can be found in \cref{sec:code_Caretaker}.\\
\includegraphics[width=1.05\textwidth]{figures/Caretaker.pdf}
 \captionof{figure}{Caretaker Pattern}
  \label{fig:figcaretaker}
\end{minipage}
\clearpage
\subsubsection{Membrane Pattern - Policies}\label{sec:membranepolicies}
Here we show the important policies for the Membrane pattern. Unlike the Caretaker pattern, a Membrane does not leak capabilities because the membrane creates deep attenuating new membranes to mask capabilities returned by its protected object, and do so also for capabilities in messages passed by its caller. A membrane that creates new membranes also creates the associated lock objects for the new membranes, and passes the capabilities of these new locks to its own associated lock object \sf{k}. Therefore when some other object calls the method \sf{lockall()}\\on the lock object \sf{k}, \sf{k} will recursively call the same method on all lock objects that it has.

Therefore, every membrane and lock object has a ghost field \sf{parent}: \begin{itemize}
\item The ghost field \sf{parent} of a membrane object \sf{m$'$} points to a membrane \sf{m} if the constructor for \sf{m$'$} is called  by \sf{m}, otherwise it points to \sf{null}
\item The ghost field \sf{parent} of a lock object \sf{k$'$} points to a lock \sf{k} if the constructor for \sf{k$'$} is called by a membrane \sf{m}, where \sf{m.lock = k}, otherwise it points to \sf{null}
\end{itemize}

@@

\begin{minipage}{\textwidth}
\subsubsection{Membrane Pattern - Illustration}\label{sec:figmem}
\small Here, we illustrate in more detail an example of the Membrane pattern. The code can be found in \cref{sec:code_Membrane}.\\
\includegraphics[width=1.05\textwidth]{figures/Membrane.pdf}
 \captionof{figure}{Membrane Pattern}
   \label{fig:figmem}
\end{minipage}
\section{Case Study of Ethereum / Solidity as a Non-OCap Model}\label{sec:ethereum}
